Binocular combination in the autonomic nervous system

### 2024-07-16 manuscript.Rmd
Edits

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
 | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: pnas.csl
header-includes:
  \usepackage{caption}
  \usepackage{lineno} \linenumbers
---

@@

Address for correspondence: Federico G. Segala, [federico.segala\@york.ac.uk](federico.segala@york.ac.uk)

Preprint server: a preprint has been deposited on BioRxiv (https://doi.org/10.1101/2024.06.04.597314) with a no reuse/adaptation without permission license

Classification: Biological Sciences - Psychological and Cognitive Sciences

Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling

@@

# Acknowledgements and funding sources

Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

>>>>

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
 | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: the-journal-of-neuroscience.csl
header-includes:
  \usepackage{caption}
  \usepackage{setspace}\doublespacing
  # \usepackage{lineno} \linenumbers
---

@@

Corresponding author: Federico G. Segala, [federico.segala@york.ac.uk](federico.segala@york.ac.uk).

Number of pages: 21

Number of figures: 4

Number of tables: 1

Number of words for abstract: 187

Number of words for introduction: 1005

Number of words for discussion: 600

Conflict of interest: The authors declare no competing financial interests.

Acknowledgements: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

\pagebreak

@@
